---
title: "TourismAcceptance - Estimation Beyond The Sample"
output: html_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r loadpackages, include=F}
library(ggplot2)
library(data.table)
library(gridExtra)
library(grid)
library(dplyr)
library(xgboost)
library(surveysd)
```

### Generate synthetic data

`sim_data` is a data set that contains data for three fictional municipalities. The columns were generated based on the distributions of the real data.

The three municipalities are:

-   001: 100 people

-   002: 1.500 people

-   003: 30.000 people

The input variables are:

+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| variable name                     | description                                                                             | source                                |
+===================================+=========================================================================================+=======================================+
| GESCHL                            | sex (1/2)                                                                               | register                              |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| GEBSTAAT_OE                       | born in Austria (0/1)                                                                   | register                              |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| GEBSTAAT_EU                       | born in the EU (0/1)                                                                    | register                              |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| STAATB_OE                         | Austrian citizenship (0/1)                                                              | register                              |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| age                               | age in years                                                                            | register                              |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| EDU_HAB_NAT                       | highest level of education (1-4)                                                        | register                              |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| einkommen                         | yearly income (€)                                                                       | Income tax and social security data   |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| einkommen_q1_anteil               | Proportion of people in the municipality who earn less than the 1st quintile in Austria | Income tax and social security data   |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| einkommen_q5_anteil               | Proportion of people in the municipality who earn more than the 4th quintile in Austria | Income tax and social security data   |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| Beruf_cat1                        | Employed in NACE08 = I55 (0/1)                                                          | Register-based census                 |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| Beruf_cat2                        | Employed in NACE08 = I56 (0/1)                                                          | Register-based census                 |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| Beruf_cat3                        | Employed in NACE08= R, H49391, H50100, H50300, N77210                                   | Register-based census                 |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| Beruf_cat0                        | Employed in any NACE08 not in (I55, I56, R, H49391, H50100, H50300, N77210)             | Structural Business Statistics Survey |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| Nachtig_pEinw                     | Number of overnight stays/municipality/inhabitant                                       | Accomodation Statistics               |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| Betriebe_pEinw                    | Number of accommodation establishments/municipality/inhabitant                          | Accomodation Statistics               |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| Betten_pEinw                      | Number of bed places/municipality/inhabitant                                            | Accomodation Statistics               |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| ASBESCH_pEinw1                    | Employees in NACE08 = I55 in municipality                                               | Structural Business Statistics Survey |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| ASBESCH_pEinw2                    | Employed in NACE08= I56 per municipality                                                | Structural Business Statistics Survey |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| ASBESCH_pEinw3                    | Employed in NACE08= R, H49391, H50100, H50300, N77210 per municipality                  | Structural Business Statistics Survey |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| ASUMS_pEinw1                      | Revenue in NACE08 = I55 in 1.000€ per municipality/person                               | Structural Business Statistics Survey |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| ASUMS_pEinw2                      | Revenue in NACE08 = I56 in 1.000€ per municipality/person                               | Structural Business Statistics Survey |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| ASUMS_pEinw3                      | Revenue in NACE08 = R, H49391, H50100, H50300, N77210 in 1.000€ per municipality/person | Structural Business Statistics Survey |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| Ankunft_pEinw_q1/\_q2/ \_q3/ \_q4 | Number of quarterly arrivals per inhabitant and municipality                            | Accommodation statistics              |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+
| G3_enc                            | **target**, "Do you think there are too many tourists in your place of residence?"      | Tourism Acceptance Survey             |
|                                   |                                                                                         |                                       |
|                                   | 1 = yes                                                                                 |                                       |
|                                   |                                                                                         |                                       |
|                                   | 0 = no                                                                                  |                                       |
|                                   |                                                                                         |                                       |
|                                   | NA = not participated in survey                                                         |                                       |
+-----------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------+

```{r loadInputData}
#read in simulated data
sim_data <- fread("sim_data.csv")

#define prediction variables
pred_vars <- c("GESCHL","GEBSTAAT_OE", "STAATB_OE", "EDU_HAB_NAT","age",
               "GEBSTAAT_EU",
               "Beruf_cat1",
               "Beruf_cat2","Beruf_cat3","Beruf_cat0",
               "Nachtig_pEinw","Betriebe_pEinw",
               "Betten_pEinw",
               "einkommen",
               "einkommen_q5_anteil","einkommen_q1_anteil","ASBESCH_pEinw1","ASUMS_pEinw1", 
               "ASBESCH_pEinw2","ASUMS_pEinw2","ASBESCH_pEinw3","ASUMS_pEinw3",
               "Ankunft_pEinw_q1","Ankunft_pEinw_q2","Ankunft_pEinw_q3","Ankunft_pEinw_q4"  
)
```

### Hyperparameter Tuning

To tune the hyperparameters of the XGBoost model, we use 5-fold Cross Validation for 60 parameter combinations to find the most suitable hyperparameter setting. We choose the parameter settings of the model with the lowest *test error*.

`survey_data` includes only data of survey participants, i.e. people we know the answer for question G3 for.

```{r tuneing, warning=FALSE}
target <- "G3_enc"
# we use the rows corresponding to survey respondents
survey_data <- sim_data[!is.na(G3_enc),]

grid <- data.table::CJ(max_depth=c(3,6,8),
                         eta=seq(0.01,0.05,by=0.01),
                         min_child_weight=c(5),
                         lambda=c(5,10),
                         alpha=c(3,5))
l <- list()

for(i in 1:nrow(grid)){
  # 5-fold CV
  #print(paste("run ",i," of ",nrow(grid)))
  g <- grid[i,]
  cv <- xgb.cv(data = as.matrix(survey_data[,..pred_vars]),
               nrounds = 300, nthread = 2, nfold = 5,
               metrics = list("logloss","error"),
               max_depth = g$max_depth, 
               eta = g$eta,
               objective = "binary:logistic",
               label=survey_data[[target]],
               weight=survey_data$weight,
               verbose = F,
               colsample_bytree=0.8,
               lambda=g$lambda,
               alpha=g$alpha,
               min_child_weight=g$min_child_weight)
  l[[i]] <- cbind(grid[i,],tail(cv$evaluation_log,1))
  remove(cv)
  gc()
}
cv_res <- rbindlist(l)

cv_res[which.min(test_error_mean),.(max_depth,eta,min_child_weight,
                                    alpha,lambda,train_error_mean,
                                    test_error_mean,
                                    test_error_std)]
message(paste("Mininum Test Error:",round(cv_res[which.min(test_error_mean),test_error_mean],3)))
min_id <- which.min(cv_res$test_error_mean)


best_max_depth <- cv_res[min_id,max_depth]  
best_eta <- cv_res[min_id,eta]
best_min_child_weight <- cv_res[min_id,min_child_weight]
best_alpha <- cv_res[min_id,alpha]
best_lambda <- cv_res[min_id,lambda]

#export best hyper params as yaml file
yaml::write_yaml(list(best_eta=best_eta,
                      best_max_depth=best_max_depth,
                      best_min_child_weight=best_min_child_weight,
                      best_alpha=best_alpha,
                      best_lambda=best_lambda,
                      min_loss=cv_res[min_id,test_error_mean]),
                 "G3_params.yaml")
```

`dat_frame` includes every person in the fictional population that did not take part in the survey. For these people we predict the probability for answering with 1 (too many tourists). The probability for anwering 0 (not too many tourists) is therefore $1-P(x=1)$.

```{r modelEstimates}
# people not included in survey
dat_frame <- sim_data[is.na(get(target)),(names(sim_data)),with=F]


weightTrain <- survey_data$weight

n_est <- 10
pred_frame <- list()
for(i in 1:n_est){
  set.seed(i)
  #print(paste("Run",i, "of",n_est))
  model_xgb <- xgboost(data = as.matrix(survey_data[,..pred_vars]), 
                       label = survey_data[[target]], 
                       max.depth = best_max_depth, 
                       eta = best_eta, 
                       nthread = 2, nrounds = 300,
                       objective = "binary:logistic",
                       eval_metric = "logloss",
                       weight = weightTrain,
                       subsample=0.8,
                       verbose=0,
                       alpha=best_alpha,
                       lambda=best_lambda,
                       min_child_weight=best_min_child_weight,
                       colsample_bytree=0.8)
  
  
  # Estimates for all people in sim_data
  ti <- Sys.time()

  x <- predict(model_xgb,as.matrix(dat_frame[,..pred_vars]))
  pred_frame[[i]] <- data.table(1-x,x,i)
  names(pred_frame[[i]]) <- c("prob_0","prob_1","run")
  Sys.time()-ti
  remove(model_xgb)
  gc()
}

pred_frame <- rbindlist(pred_frame)
pred_frame[,ID:=rep(1:nrow(dat_frame), n_est)]
dt_mean <- pred_frame[, lapply(.SD, mean), by = ID, .SDcols = 1:2]
dt_mean[,ID:=NULL]

#check rowsums sum up to 1
stopifnot(all(rowSums(dt_mean)-1<0.0001))

dat_frame <- cbind(dat_frame,dt_mean)

# we get one probability of answering "too many" for every person in the survey sample scope
# -> prob_1: Probability of answering "too many"
# -> prob_0: Probability of not answering "too many" (1-prob_1)
# survey part will have probability 1 for their respective answer, 0 else
temp <- survey_data[,.(ID,get(target))]
temp <- dcast(melt(temp, id.vars="ID"), ID ~ variable+value, length)
setnames(temp,c("V2_0", "V2_1"),
         paste0("prob_",0:1))
survey_dat <- merge(survey_data,temp,by="ID")

# concatenate unit estimates with "real" answers from survey
dat_pred <- rbind(survey_dat,dat_frame)
```

Now we aggregate the estimates (proportion of people thinking "too many tourists") on municipality level. For this we take the mean of the probabilities over all people per municipality.

For survey respondents this probability is 1 for their answer and 0 else. For non-participants this probability is according to the xgboost model.

```{r aggregateEstimates}
area_est <- dat_pred[,sum(prob_1)/.N,by=areaID]
names(area_est) <- c("areaID","estimator_too_many")
area_est
```

Next we draw the bootstrap samples (100). `bw` is a data.table containing the origial data of the survey data (input variables, weight, ID etc.) for all survey participants, plus 1000 bootstraped weights per person.

We use the `draw_bootstrap` function from the surveysd package. In our project we use 1000 bootstrap replicates. To reduce run time for the example, we only use 100.

```{r bootstrap}
#draw bootstrap weights
n_boot <- 100
tmp <- copy(survey_data)
tmp[,NstrataVar:=sum(weight),by=strata] 
setnames(tmp,"strata","strataxx")
bw <- draw.bootstrap(tmp , strata="strataxx",
                     weight="weight",
                     pid = "ID",
                     totals = "NstrataVar",
                     REP = n_boot)
# our original data set with 1000 bootstrapped weights (cols w1-w1000)
dim(bw)
```

We calculate 100 bootstrap estimates per area. The process is the same as the estimation of %-too-many above.

```{r bootstrapEstimates}
res <- list()
y_xgb <- bw[,get(target)]

#iterate over w<i> columns
for(i in 1:n_boot){
  if(i %% 10 == 0){
    print(paste("run",i,"of",n_boot))
  }
  weightTrain <- bw[,get(paste0("w",i))]
  model_xgb2 <- xgboost(data = as.matrix(bw[,..pred_vars]),
                        label = y_xgb, 
                        max.depth = best_max_depth, 
                        eta = best_eta,
                        lambda = best_lambda,
                        alpha = best_alpha,
                        min_child_weight = best_min_child_weight,
                        nthread = 4, nrounds = 300,
                        objective = "binary:logistic",
                        weight = weightTrain,
                        eval_metric = "logloss",
                        verbose = 0)
  
  pred_frame <-  predict(model_xgb2,as.matrix(dat_frame[,..pred_vars]))
  preds_frame1 <- data.table(prob_1=pred_frame)
   
  
  preds_frame <- cbind(dat_frame[,!c("prob_1","prob_0")],preds_frame1)
  preds_frame[,prob_0:=1-prob_1]
  
  
  dat_pred <- rbind(survey_dat,preds_frame)
  dat_pred[,":="("prop_too_many"=sum(prob_1)/.N,"prop_other"=sum(prob_0)/.N,
                 "n_population"=.N),by="areaID"]
  
  res[[i]] <- unique(dat_pred[,.("run"=i,areaID,prop_too_many,prop_other,n_population)])
  
  remove(list=c("model_xgb2","dat_pred","pred_frame","preds_frame","preds_frame1"))
  gc()
}
n_boot <- length(res)
res <- rbindlist(res)
```

Now we look at the standard deviation per area over all bootstrap estimates.

```{r sdAreaID}
# Standard deviation per area
sd_per_area <- res[,.("SD_too_many"=sd(prop_too_many)),by=areaID]
sd_per_area
```

We construct the confidence intervall (CI) by finding the 2.5 and 97.5-Quantile of the bootstrap estimates.

```{r getCI}
res1 <- dcast(run~areaID,data=res[,(c("areaID","prop_too_many","run")),with=F],
              value.var = "prop_too_many")
res1 <- as.data.table(apply(res1[,!"run"],2,sort))

quant2_5 <- res1[ceiling((nrow(res1))*0.025),]
quant97_5 <- res1[ceiling((nrow(res1))*0.975),]

quant_area <- data.table(areaID=1:3,q2_5=unlist(quant2_5),q97_5=unlist(quant97_5))
quant_area[,CI_width:=q97_5-q2_5]
quant_area

area_est <- merge(area_est,quant_area, by="areaID")
area_est
```

Estimates for areas with a CI\>10 are suppressed and will not be published.

```{r suppress}
area_est[,error_FLAG:=0]
area_est[CI_width>0.1,error_FLAG:=1]
sum(area_est$error_FLAG)
```

Our estimates can range from 0 to 1 (or 0% to 100%). We break this range into intervals of 10, e.g. 0-10%, 11-20%,...

Only the interval the estimator lies in is published.

```{r}
area_est[,perc_too_many:=round(estimator_too_many,4)*100]
area_est[,"perc_too_many_INT":=fcase(perc_too_many<=10,"0-10%",
                                     perc_too_many>10&perc_too_many<=20,"11-20%",
                                     perc_too_many>20&perc_too_many<=30,"21-30%",
                                     perc_too_many>30&perc_too_many<=40,"31-40%",
                                     perc_too_many>40&perc_too_many<=50,"41-50%",
                                     perc_too_many>50&perc_too_many<=60,"51-60%",
                                     perc_too_many>60&perc_too_many<=70,"61-70%",
                                     perc_too_many>70&perc_too_many<=80,"71-80%",
                                     perc_too_many>80&perc_too_many<=90,"81-90%",
                                     perc_too_many>90,"91-100%")]
area_est
```
